Project Notes

### 2020-04-18 notes/notes.tex
Notes: update 18/04/2020

>>>>

\paragraph{18/04/2020}
\begin{itemize}
\item
Implement utility tool to: (1) parse existing type declarations
from Scribble file, (2) extract user custom types,
(3) insert missing TypeScript primitive types, before proceeding
with normal workflow.

\item
Adapt EFSM API -- previously, I use a metadata dictionary
to store the protocol name and role name. Now that I need to
propagate the custom type information too, I have a new 
\texttt{Endpoint} API which holds the EFSM (without metadata)
and the protocol/role name is lifted as a property of the 
endpoint API. Jinja templates have been adapted with the
API change.
\end{itemize}
